The Journey from Wild to Text Book Data: A Case Study of the National Longitudinal Survey of Youth

### 2021-05-05 report_alt.Rmd
create two subsections in The NLSY79 section i.e Database and Target Data.

@@

@@

Finally, we saved the imputed data and set the appropriate data type for the variables. We also saved the NLSY79 cohort's demographic information and the high school dropout cohort in a separate data sets. Here, we defined high school dropouts as respondents who only completed either $9^{th}$, $10^{th}$, $11^{th}$ grade, or who completed $12^{th}$ when their age are at least 19 years old (means that these IDs being dropped out in certain year, but they returned back to high school to complete it). We also filtered the data to be only male and aged between 14 and 17 years old to refresh the high school dropouts data in the `brolgar` package.

We then make these three data sets and its processing documentation to be publicly available through an R data container package called `yowie`. The complete flow from the raw data to these data set is displayed in Figure \ref(fig:flowchart).

>>>>

## Database

@@

## Target Data

As mentioned in Section 1, this paper aims to refresh the NLSY79 data as used in Singer and Willet's text book (@SingerJudithD2003Alda). This data set contains the information of yearly mean hourly wages from the NLSY79 cohort, with education and race as covariates. This data set represents the measurement of male high-school dropouts, aged from 14 to 17 years old when first time measured. Hence, in this paper, after getting the data set of high school graduates, we subset it by only having the high school dropouts.

Since there is no information of high school drop-outs in Singer and Willet's book, we define high school dropouts as respondents who only completed either $9^{th}$, $10^{th}$, $11^{th}$ grade, or who completed $12^{th}$ when their age are at least 19 years old (means that these IDs being dropped out in certain year, but they returned back to high school to complete it).

@@

Finally, we saved the imputed data and set the appropriate data type for the variables. As our target data is the mean hourly wage of the high-school dropouts, we then subset the high-school graduate data set to be only having the male-high school dropout data. We also saved the NLSY79 cohort's demographic information in a separate dataset. We then make these three data sets and its processing documentation to be publicly available through an R data container package called `yowie`. The complete flow from the raw data to these data set is displayed in Figure \ref(fig:flowchart).
